---
title: "Homework 1"
author: "Rachel Lee"
date: "9/20/2019"
output: github_document
---

```{r Library}
library(tidyverse)
```

# Problem 1
## create dataframe

```{r}
# Creating dataframe
set.seed(10)
problem1_df= tibble(
  random = rnorm(8),
  vec_logical = random > 0,
  vec_char = c("a", "c", "f", "g", "k", "i", "p", "h"),
  vec_factor = as.factor(c("m","f","o","m","m","f","o","f"))
)
#we got a numeric value 
mean(problem1_df$random) 

#we got a numeric value 
mean(problem1_df$vec_logical)

#we did not get a numeric value because it is a character vector
mean(problem1_df$vec_char)

#we did not get a numeric value because it is a non-numeric factor vector
mean(problem1_df$vec_factor)

#coercing character vector as numeric vector, we do not get a mean
mean(as.numeric(problem1_df$vec_char))

#coercing factor vector as numeric vector, we get a mean 
mean(as.numeric(problem1_df$vec_factor))

```
#creating the second code chunk: multiplying variables


```{r Problem_1part2, warning=FALSE}
# Problem_1part2

# Coerce logical vector as numeric, then multiply with random variables
as.numeric(problem1_df$vec_logical)*(problem1_df$random)

# Coerce logical vector as factor, then multiply with random variables
as.factor(problem1_df$vec_logical)*(problem1_df$random)

# Coerce logical vector as a factor vector, then coerce it as a numeric vector, then multiply with random variables
as.numeric(as.factor(problem1_df$vec_logical))*(problem1_df$random)
```



# Problem 2

## Creating ggplots

### Creating a new dataframe

```{r Problem2, warning=FALSE}
# Creating dataframe
set.seed(1)
problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = c(x + y > 1),
  vec_numeric = c(vec_logical),
  vec_factor = c(vec_logical)
)
```


### A short description of the dataframe

* The number of rows in the dataframe is **`r nrow(problem2_df)`**.
* The number of columns in the dataframe is **`r ncol(problem2_df)`**.
* The mean, median, and standard deviation of *x* are **`r mean(problem2_df$x)`, `r median(problem2_df$x)` and `r sd(problem2_df$x)`** respectively
* The proportion of cases for which the logical vector(x + y > 1) is true: **`r length(problem2_df$vec_logical[which(problem2_df$vec_logical == 'TRUE')]) / nrow(problem2_df)`**.


### Use the dataframe **problem2_df** and create scatter plots

```{r scatter_plot, warning=FALSE}

# Create a scatter plot of the logical vector
ggplot(problem2_df, aes(x = x, y = y, color = vec_logical)) + geom_point()

# Save the ggplot as a PNG file
ggsave(filename = "C:/Users/shvar/OneDrive/Desktop/problem2_df_color_logical_ggplot.png")


# Creating a scatter plot using the numeric vector
ggplot(problem2_df, aes(x = x, y = y, color = vec_numeric)) + geom_point()
# Creating a scatter plot using the factor vector
ggplot(problem2_df, aes(x = x, y = y, color = vec_factor)) + geom_point()
```


